% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Yiheng Zhi}

\basicInfo{
  \email{snophy3@126.com} \textperiodcentered\ 
  \phone{(+86) 138-167-12921} \textperiodcentered\ 
}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{East China University of Science and Technology} - Shanghai, China}{2017 -- 2021}
\textit{B.S.} in Computer Science and Technology

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Bytedance} - Shanghai, China}{Oct. 2020 -- Present}
\role{Software Engineer \& Software Engineer Intern}{}
\textbf{Supplier Chain Management System}
\newline
The platform enables game studios, buyers and many more business partners having a customized supplier chain management for game industry.
\begin{itemize}
  \item Role: Back-end Developer
  \item Implemented features: Setting up \textit{Business Plan}; Managing \textit{Request for Quote}; Submitting \textit{Payment Request} and etc.
  \item Optimized performance: Applying multi-thread(goroutine) , message queue and FaaS(Function as a Service).
  \item Enhanced code readability: Applying AOP(Aspect-Oriented Programming) and dependency injection.
  \item Troubleshot live-site issues: Analyzing error logs, CPU \& memory usage and RPC success rate through APM(Application Performance Monitor).
\end{itemize}
\textbf{Game AI Automation}
\newline
Customize AI models for various game products. The project mainly used in automated testing.
\begin{itemize}
  \item Game Category: Cards, Shooting.
  \item Algorithm: Reinforcement learning (Q-learning, DQN); Imitation Learning.
  \item Deployment: Docker.
  \item Framework: Tensorflow, Pytorch, Dlib, OpenCV.
\end{itemize}

\datedsubsection{\textbf{Electronic Arts (EA)} - Shanghai, China}{Jul. 2020 -- Sep. 2020}
\role{Software Engineer Intern}{}
\textbf{API Testing Web Tool}
\newline
A web application for Product Manager and QA for API testing and monitoring.
\begin{itemize}
  \item Role: Full-Stack Developer
  \item Programming Language: Java, Javascript
  \item Framework: Springboot, React
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Golang, C++, Python, Shell, Java, Javascript, HTML, CSS
  \item Web Development: Gin, Kitex, Springboot, React, Django
  \item Machine Learning: Pytorch, Tensorflow, Dlib
  \item Database: MongoDB, MySQL, Redis
  \item Operating System: Linux
  \item Source Code Management: git
  \item Low Latency Technology: OpenMP, libgo
  \item Design Pattern: Singleton, Factory, Interface
  \item Project Management: Scrum
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textbf{\nth{2} Prize}, National Olympiad in Informatics in Provinces}{Dec. 2014}
\datedline{\textbf{\nth{1} Prize}, National Olympiad in Informatics in Provinces}{Dec. 2015}
\datedline{\textbf{Successful Participant}, NOI2016 Winter Camp}{Jan. 2016}
\datedline{\textbf{\nth{1} Prize}, National Olympiad in Informatics in Provinces}{Dec. 2016}
\datedline{\textbf{Bronze Medal}, ACM-ICPC Asia Regional Contest \textit{(Qingdao Site)}}{Nov. 2018}
\datedline{\textbf{Silver Medal}, ACM-ICPC Asia Regional Contest \textit{(Jiaozuo Site)}}{Nov. 2018}
\datedline{\textbf{Silver Medal}, ACM-ICPC Asia Regional Contest \textit{(Shanghai Site)}}{Nov. 2019}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Languages: English - Fluent, Chinese Mandarin - Native
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
